Bayesian Rate Estimation

### 2012-08-01 many.tex
Abstract improvements; updated to match current paper.

\begin{abstract}
  We show how to obtain a Bayesian estimate of the rate of signal
  events from a set of signal and background events indexed by a
  ranking statistic when the shapes of the signal and background
  distributions are known, can be estimated, or approximated.  We
  focus on the specific application of estimating astrophysical rates
  of the coalescence of compact binary black holes or neutron stars
  from a set of triggers in the LIGO/Virgo gravitational wave
  detectors, but our framework is fully general.  We discuss the
  systematic effects on the rate estimate due to differences between
  the assumed and true shapes of the foreground or background
  distributions, identifying ways these effects can be minimized.
  Similarly, we discuss the effects of various priors on the rate,
  including uninformative priors, weakly-informative priors, and the
  use of priors from previous rate experiments.  In the limit where
  the expected signal rate gives high probability of zero or one
  signal in the data, our technique reduces to the ``loudest event
  statistic,'' but it is generally applicable to arbitrarily large
  signal rates.
\end{abstract}

>>>>

\begin{abstract}
  We show how to obtain a Bayesian estimate of the rate of signal
  events from a set of signal and background events when the shapes of
  the signal and background distributions are known, can be estimated,
  or approximated; our method works well even if the foreground and
  background event distributions overlap significantly.  We give
  examples of determining the rates of gravitaitonal wave events in
  the presence of background triggers from a template bank when noise
  parameters are known and/or can be fit from the trigger data.  We
  also give an example of determining globular cluster shape and
  location parameters from an observation of a stellar field that
  contains a non-uniform background density of stars superimposed on
  the cluster stars.
\end{abstract}
